---
title: "NHANES Metadata"
output:
  html_document:
    df_print: paged
---

Load the *nhanesA* library (v0.7.2 from GitHub).
```{r}
library(devtools)
install_github("cjendres1/nhanes")
library(nhanesA)
```

Get metadata about NHANES tables from all survey years and data groups.
```{r}
get_all_tables <- function() {
  data_groups <- c("DEMOGRAPHICS", "DIETARY", "EXAMINATION", "LABORATORY", "QUESTIONNAIRE")
  survey_years <- c(1999, 2001, 2003, 2005, 2007, 2009, 2011, 2013, 2015, 2017)
  all_tables <- c()
  for (year in survey_years) {
    for (data_group in data_groups) {
      tables_year <- get_tables(data_group=data_group, year=year)
      all_tables <- rbind(all_tables, tables_year)
    }
  }
  return(all_tables)
}

get_tables <- function(data_group, year) {
  tables <- nhanesTables(data_group=data_group, year=year)
  tables$Data.Group <- c(data_group)
  tables$Data.Year <- c(year)
  return(tables)
}
```

Get the metadata about all the NHANES tables. Print it out. Write to a CSV file.
```{r}
output_folder <- "metadata/"
dir.create(file.path(".", output_folder), showWarnings=FALSE, recursive=TRUE)
all_tables <- get_all_tables()
write.csv(all_tables, paste(output_folder, "nhanes_tables.csv", sep = ''), row.names=FALSE)
```

Get metadata about all variables in the given collection of NHANES tables.
```{r}
get_all_variables <- function(tables) {
  details_folder = paste(output_folder, "response_metadata/", sep="")
  dir.create(file.path(".", details_folder), showWarnings=FALSE, recursive=TRUE)
  all_variables <- data.frame(matrix(ncol = 5, nrow = 0))
  colnames(all_variables) <-c("Variable Name", "SAS Label", "English Text", "Target", "Table")
  variables_metadata_table <- paste(output_folder, "nhanes_variables.csv", sep="")
  write.table(all_variables, variables_metadata_table, row.names=FALSE, sep=",")
  for (nhanes_table in 1:nrow(tables)) {
    table_name <- tables[nhanes_table, 'Data.File.Name']
    data_group <- tables[nhanes_table, "Data.Group"]
    table_variables <- get_variables_in_table(table_name = table_name, 
                                              nhanes_data_group = data_group, 
                                              response_details_folder = details_folder)
    write.table(table_variables, file=variables_metadata_table, sep=",", 
                append=TRUE, col.names=FALSE, row.names=FALSE)
  }
}
```

Get metadata about the variables in the given NHANES table (specified by the table name) and data group.
```{r}
get_variables_in_table <- function(table_name, nhanes_data_group, response_details_folder) {
  all_variables <- data.frame(matrix(ncol = 5, nrow = 0))
  colnames(all_variables) <-c("Variable Name", "SAS Label", "English Text", "Target", "Table")
  # Get all variables in this table
  table_variables <- nhanesTableVars(data_group=nhanes_data_group, 
                                     nh_table=table_name, details=TRUE, 
                                     nchar=1024, namesonly=FALSE)
  # For each variable in this table get its details
  if(length(table_variables) > 0) {
    for (variable in 1:nrow(table_variables)) {
      variable_name <- table_variables[variable, 'Variable.Name']
      tryCatch({
        variable_details <- nhanesCodebook(nh_table = table_name, variable_name)
        name <- clean(variable_details['Variable Name:'])
        label <- clean(variable_details['SAS Label:'])
        text <- clean(variable_details['English Text:'])
        target <- clean(variable_details['Target:'])
        variable_details_vector <- c(name, label, text, target, table_name)
        all_variables[nrow(all_variables) + 1, ] <- variable_details_vector
        response_options <- variable_details[length(variable_details)]
        out_file <- paste(response_details_folder, name, ".csv", sep = "")
        write.csv(response_options, file=out_file, row.names=FALSE)
      }, error=function(e) {
        cat("ERROR: ", conditionMessage(e), "\n")
        cat("Variable: ", variable_name, ". Table: ", table_name, "\n")
      })
    }
  }
  return(all_variables)
}

# Remove carriage return, new line, comma, backslash and quote characters
clean <- function(text) {
  text <- gsub("[\r\n,\\\"]", "", text)
  return(text)
}
```

Get metadata about all variables in all the NHANES tables collected above. The metadata will be written to a variable metadata table.
```{r}
get_all_variables(all_tables)
```
